Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-09-19 manuscript/manuscript.tex
Modification in manuscript: added new exponential variation with b figures

Because the constant $b$ controls the variation of the density function, we wanted to test how does the accuracy of the method behaves at different values of $b$.
We computed the difference between the Marussi tensor component $g_{zz}$ generated by the numerical model on the big grid of 30$^\circ\times$30$^\circ$ (see Table \ref{tab:grids}) and the analytical solution.
For each value of $b$ we calculated these difference for the same set of values of $D$ we've been using on the previous tests, obtaining one curve for each kind of variation.

This tests were performed using both the thin and the thick spherical shell, whose results can be seen in Figure \ref{fig:D-exp-power}.
Taking into account that lower values of $b$ implies a more varying function, we can see that for extremely varying functions the numerical model does not perform well: for $b$=100m the difference is almost 100\% in the thin shell case, and the same happens with $b$=10km in the thick shell case.

On both cases, the model performs under the acceptable threshold for values of $b$ greater than the thickness of the shell, in other words, when the absolute value of the exponent in equation \ref{eq:density-exp} is lower than 1.
Although this sets a limitation to the model, the maximum acceptable variation is very far from real density distributions inside the Earth.
For example, if we take into account a tesseroid with 35km of thickness, a density of 2670kg/m$^3$ on its top surface and $b=35$km, then the density at its bottom will be approximately of 7000kg/m$^3$, very far from the values we can find at such depths.

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/Dexp-power-differences.pdf}
\caption{
    Differences between the Marussi tensor component $g_{zz}$ generated by the numerical model and the analytical solution for (a) a thin spherical shell of 1km of thickness and (b) a thick sphericall shell of 35km of thickness, both with the exponential density defined on equation \ref{eq:density-exp} with different values of $b$. Each computation was performed on the big grid described in Table \ref{tab:grids}, for different values of the distance-size ratio $D$. Each curve corresponds to a value of $b$. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-exp-power}
\end{figure}

>>>>

Because the constant $b$ controls the variation of the density function, we wanted to test how does the accuracy of the method behaves at different values of $b$.
In order to do this we proposed a set of density functions, each one with a different value of $b$ and normalised in such way that they reaches a density of 2900 kg/m$^{3}$ at the bottom of the spherical shell.
We computed the difference between the Marussi tensor component $g_{zz}$ generated by the numerical model on the big grid of 30$^\circ\times$30$^\circ$ (see Table \ref{tab:grids}) and the respective analytical solution.
These differences were calculated for each proposed density function and for the same set of values of $D$ we have been using on the previous tests, obtaining one curve for each value of $b$.

This tests were performed using both the thin and the thick spherical shell.
On Figures \ref{fig:D-exp-power-thin}a and \ref{fig:D-exp-power-thick}a we can see the density functions used to perform these tests for each spherical shell model, respectively, and their results can be seen in \ref{fig:D-exp-power-thin}b and \ref{fig:D-exp-power-thick}b.
Taking into account that lower values of $b$ implies a more varying function, we can see that for extremely varying functions the numerical model does not perform well: for $b$=100m the difference is almost 100\% in the thin shell case, and the same happens with $b$=10km in the thick shell case.

On both cases, the model performs under the acceptable threshold for values of $b$ greater than the thickness of the shell, in other words, when the absolute value of the exponent in equation \ref{eq:density-exp} is lower than one.
Although this sets a limitation to the model, the maximum acceptable variation is very far from real density distributions inside the Earth.
For example, if we take into account a tesseroid with 35km of thickness, a density of 2670kg/m$^3$ on its top surface and $b=35$km, then the density at its bottom will be approximately of 7000kg/m$^3$, very far from the values we can find at such depths.

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/Dexp-power-differences-thin.pdf}
\caption{
    Results of the accuracy tests for different exponential density functions in case of a thin spherical shell (1km of thickness).
    (a) Density functions used in the tests, each one with a different value of $b$ and normalised in such way that they reaches a density of 2900kg/m$^{3}$ at the bottom of the shell.
    (b) Differences between the Marussi tensor component $g_{zz}$ generated by the numerical model and the analytical solution for each density function. Each computation was performed on the big grid described in Table \ref{tab:grids}, for different values of the distance-size ratio $D$. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-exp-power-thin}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/Dexp-power-differences-thick.pdf}
\caption{
    Results of the accuracy tests for different exponential density functions in case of a thick spherical shell (35km of thickness).
    (a) Density functions used in the tests, each one with a different value of $b$ and normalised in such way that they reaches a density of 2900kg/m$^{3}$ at the bottom of the shell.
    (b) Differences between the Marussi tensor component $g_{zz}$ generated by the numerical model and the analytical solution for each density function. Each computation was performed on the big grid described in Table \ref{tab:grids}, for different values of the distance-size ratio $D$. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-exp-power-thick}
\end{figure}
